### 2017-04-05 paper/oopsla17-submission/evaluation-accuracy.tex
eval

\paragraph{Our Classifiers}
We evaluate five classifiers, each trained on the full set of features.
% features: 44 local syntactic features, 176 contextual syntactic
% features, 55 typing features, and a single expression size feature.
% %
% \ES{should explain the make-up of these groups}
%
% We preemptively discard expressions that are not part of the minimal
% type error slice --- we will explain the rationale for this in
% \autoref{sec:feature-utility} --- and thus the final feature count is
% 276.
%
Our classifiers are:
%
\begin{enumerate}
\item A logistic regression trained with a learning rate
  $\eta = 0.001$, an L2 regularization rate $\lambda = 0.001$, and a
  mini-batch size of 200.
\item A decision tree trained with the \ES{HUMA?} algorithm and \ES{HUMA: hyperparams?}.
\item A random forest trained with the \ES{HUMA?} algorithm and 30 estimators \ES{HUMA: hyperparams?}.
\item Two multi-layer perceptron neural networks, both trained with $\eta = 0.001$,
  $\lambda = 0.001$, and a mini-batch size of 200. The first MLP
  contains a single hidden layer of 10 neurons, and the second contains
  a hidden layer of 500 neurons. This allows us to investigate how well
  the MLP can \emph{compress} its model (cf.~\cite{FIXME}).
\end{enumerate}
%
All classifiers were trained for 20 epochs on one dataset
--- \ie they were shown each program 20 times ---
before being evaluated on the other.

>>>>

\paragraph{Our Classifiers}
We evaluate five classifiers, each trained on the full set of features.
% features: 44 local syntactic features, 176 contextual syntactic
% features, 55 typing features, and a single expression size feature.
% %
% \ES{should explain the make-up of these groups}
%
% We preemptively discard expressions that are not part of the minimal
% type error slice --- we will explain the rationale for this in
% \autoref{sec:feature-utility} --- and thus the final feature count is
% 276.
%
Our classifiers are:
%
\begin{enumerate}
\item A logistic regression trained with a learning rate
  $\eta = 0.001$, an $L_2$ regularization rate $\lambda = 0.001$, and a
  mini-batch size of 200.
\item A decision tree trained with the \ES{HUMA?} algorithm and \ES{HUMA: hyperparams?}.
\item A random forest trained with the \ES{HUMA?} algorithm and 30 estimators \ES{HUMA: hyperparams?}.
\item Two multi-layer perceptron neural networks, both trained with $\eta = 0.001$,
  $\lambda = 0.001$, and a mini-batch size of 200. The first MLP
  contains a single hidden layer of 10 neurons, and the second contains
  a hidden layer of 500 neurons. This allows us to investigate how well
  the MLP can \emph{compress} its model (cf.~\cite{FIXME}). The neurons
  use rectified linear units (ReLU) as their activation function, a
  common practice in modern neural networks.
\end{enumerate}
%
All classifiers were trained for 20 epochs on one dataset
--- \ie they were shown each program 20 times ---
before being evaluated on the other.
%
The logistic regression and MLPs were trained with the \textsc{Adam}
optimizer \ES{CITE}, a variant of stochastic gradient descent that has
been found to converge faster.
